Almost compatible functions and infinite length games

### 2016-02-03 articles/almost-compatible-functions-and-topological-games/article.tex
near final draft of alcomp paper

  \begin{game}
    Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\),
    \(\pl F\).
    In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by
    \(\pl F\)
    choosing subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).

@@

  This characterization is slightly different than the typical characterization
  in which the second player first chooses a specific
  finite subcollection \(\mc F_n\) of the cover itself and lets
  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
  in \cite{MR1378387}.
  However, it's easily seen that these games are equivalent
  for perfect information strategies (so both characterize
  the Menger property), and this characterization is
  more convenient for our concerns.

@@

  But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.
  We take the following lemma from Kunen.

 \begin{lemma}[\cite{MR597342}]
    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
    regarded as forcing with
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(V[G_\mu]\).
    Let \(\dot n,\ddot n\) be a
    \(\operatorname{Fn}(\omega_2,2)\)-,
    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
    for \(A\subseteq\omega\), there is a canonical
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
    \[
      \ddot A
        =
      \{
        (\ddot n,p\rest [\mu,\omega_2))
      :
        (\dot n,p)\in \dot A
      \}
    \]
    which satisfies
    \(
      A
        =
      \operatorname{val}(\dot A,G)
        =
      \operatorname{val}(\ddot A,G_\mu)
    \).
  \end{lemma}

  \begin{theorem}
    It follows from the consistency of \(ZFC\) that
    there exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
    and \(\neg\alcompS{\aleph_2}\).
  \end{theorem}

  \begin{proof}
    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\) into
    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
    of the universe containing \(\mb P\) such that
    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).

    Let \(\lambda\) be the ordinal \(M\cap \omega_2\).
    We may assume
    \(
      \dot f_{[\lambda,\lambda+\omega)}
        =
      \{
        ((\lambda+k_p,m_p)^\cdot, p)
      :
        p\in C
      \}
    \)
    for some countable \(C\subseteq\operatorname{Fn}(\omega_2,\omega)\).
    Let
    \(
      \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        =
      \bigcup_{p\in C}\operatorname{dom} p
    \).

    Let \(\delta_\lambda\) denote the order type of
    \(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})\setminus \lambda\),
    and for \(\mu\leq\lambda\) let \(\varphi_{\mu,\lambda}'\) be the
    order-preserving bijection from
    \(
      \mu\cup
      \left(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        \setminus
      \lambda\right)
    \)
    onto the ordinal \(\mu+\delta_\lambda\).
    This lifts canonically to an order-preserving bijection
    \(
      \varphi_{\mu,\lambda}
        :
      \operatorname{Fn}(\mu\cup Y,2)
        \to
      \operatorname{Fn}(\mu+\delta,2)
    \).

    Consider the \(\mb P\)-name
    \(
      F_M
        =
      \{
        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
      :
        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_A
      \}
    \).

    % Other values
    %         replacing \(\lambda>\mu\) will result in their own set \(Y\)
    %         and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
    %         assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
    %         is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
    %         intersected with
    %         \(\alpha\) is contained in \(\mu\).

            Now the object \(F_M\) is an
            element of \(M\), and \(M\) believes this statement is true:
            \[
            (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
            \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
            \cap \lambda\subset \mu \ \ \mbox{and}\ \
            F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\]

            But now, this  means that,
            not only is there  an \(\alpha\in M\),
            \( F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})\)
            but also that there is an increasing sequence
             \(\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda\) of
             such \(\alpha\)'s satisfying that, for each \(\xi\)
            we have that \(\operatorname{supp}(\dot
            f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is contained in \(\alpha_{\xi+1}\).

            Choose such a sequence.
             This means that if we let \(A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)\) we
             have the name \(\dot f_A\) in \(M\). This then means that all
             the \(( (\beta,m) , p)\) appearing in \(\dot f_A\) have the property
             that \(\mathop{dom}(p)\) is contained in \(M\).
            There is, within \(M\), a name \(\dot g\) satisfying that
             \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
            for all \(k >\dot g(n)\).

            \bigskip

            We now apply the above Lemma using \(\mu = \mu_0\) and we are now
            working in the extension \(V[G_\mu]\). We will abuse the notation
            and use \(\dot f_{[\alpha_n,\alpha_n+\omega)}\) instead of
              \(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})\) as defined in
              the Lemma.
            We work for a contradiction. Something special has now happened,
             namely,  the supports of the names \(\{
            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}\) are pairwise disjoint
            and also disjoint from the support of the name
             \(\dot f_{[\lambda,\lambda+\omega)}\) (under the same convention about
             \(G_\mu\).  And not only that, these names are pairwise isomorphic (in
             the way that they all map to \(F_M\)).

            \bigskip

            Since \(A\) is disjoint from \([\lambda,\lambda+\omega)\),
            there must be an integer \(\ell\)
            together with a condition
             \(q\in \mathop{Fn}(\omega_2\setminus \mu,2)\) satisfying that for all
             \(n>\ell\) , \(q\) forces that

            \centerline{
             ``if \(k>\dot g(n)\) (since  \(\alpha_n+k\in A\)) then
             \(\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
            \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)\)''.}

            Choose \(n\) large enough so that \(\mathop{dom}(q) \cap [\alpha_n,
            \mu_{n+1})\) is
            empty.
             Choose \(q_1<q\restriction \lambda\) (in \(M\)) so that
            \[ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
             \dot f_{[\alpha_n,\alpha_n+\omega)}) =
            \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
             \dot f_{[\lambda,\lambda+\omega)}) \]
            and then (again in \(M\)) choose \(q_2 < q_1\)
            so that it both forces a value
             \(L\) on \(\ell+\dot g(n)\)
            and subsequently forces a value \(m\) on
             \(\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)\).
            But now, again calculate
            \[ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
            (q_2\restriction \operatorname{supp}(\dot
            f_{[\alpha_n,\alpha_n+\omega)}))\]
            and, by the isomorphisms, we have that \(q_3\) forces that
             \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m\).

            Technically (or with more care)  all of this is taking place in the
            poset \(\operatorname{Fn}(\omega_2\setminus \mu,2)\) and this means
            that \(q_3\) and \(q\) are all compatible with each other.

            Follow
            the bouncing ball: it suffices to consider
             \(q(\beta)=e\) and to assume that \(q_3(\beta)\) is defined.
            Since \(q_3(\beta)\) is defined, we have that
            there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
            and that \(q_3(\beta) = q_2(\beta')\).
            But, by definition of \(q_1\), \(\beta'\in\mathop{dom}(q_1)\)
            and even  that \(q_1(\beta') = q(\beta)\).
             Then, since \(q_2<q_1\), we have that \(q_2(\beta')=q_1(\beta') =
             q(\beta)\). This completes the circle that \(q_3(\beta) = q(\beta)\).
            \bigskip

            Finally, our contradiction is that \(q_3\cup q_2\cup q\)
            forces that
             \(k=L+1\) violates the quoted statement above.
            \end{proof}

@@

            \bigskip

@@

            \bigskip

            \newpage

@@

  Note that Question \ref{mainQuestion} remains unsolved; however,
  our results have revealed that we cannot hope to find a \(ZFC\)
  counterexample where \(X=\oneptlind\kappa\). This is
  because if we also assume \(V=L\), it follows that
  \(\alcompSP{\kappa}\) and therefore \(\pl F\kmarkwin2\menGame{X}\)
  for every cardinal. Although, one may consider the following weaker question.

@@

  % \section{Generalized Kurepa families and almost-compactible functions}

  % TODO

>>>>

  \begin{game}
    Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\),
    \(\pl F\).
    In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by
    \(\pl F\) choosing a
    subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).

@@

  This characterization is slightly different than the typical characterization
  in which the second player first chooses a specific
  finite subcollection \(\mc F_n\) of the cover itself and lets
  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
  in \cite{MR1378387}.
  However, it's easily seen that these games are equivalent
  for perfect information strategies (so both characterize
  the Menger property in the same way), and this characterization is
  more convenient for our concerns.

@@

  But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.

            The forcing extension of a model $M$ by a poset $\mathbb P\in M$ is
            obtained simply by evaluating all $\mathbb P$-names from $M$ by a
            generic filter $G$.
             A set $\tau$ is a $\mathbb P$-name if $\tau$ is a
             (possibly empty)
            set of ordered pairs $(\sigma,p)$ where $p\in \mathbb P$ and
             $\sigma$ is also itself a $\mathbb P$-name.
            If $G$ is a $\mathbb P$-generic filter, then
             $\val_G(\tau) $ is defined to equal
              $\{ \val_G(\sigma) : ~~(\exists p\in G)~~(\sigma,p)\in \tau\}$.

            If $x\in M$, then the canonical
            $\mathbb P$-name, $\check x$, is generally, and recursively,
             taken to be
             $\{ (\check y, 1) : y\in x\}$ where $1$ is the maximum element of
             $\mathbb P$.  However, it will be convenient to consider, when the
            context is clear, $(x,p)$ (for any $p\in \mathbb P$)
            to be a kind of $\mathbb P$-name.
            In particular
            if $\tau \subset X\times \mathbb P$ (for some fixed $X\in M$),
            then we may let $\tau[G] = \{ x : ~~(\exists p\in
            G)~~(x,p)\in\tau\}$.

            Thus,  $\val_G(\tau)$ will denote the recursive evaluation by $G$ and
             $\tau[G]$ will be defined as above.
            In fact, if $\tau\in M$ is any set then each of
             $\val_G(\tau)$ and $\tau[G]$ are well defined.
            It is a standard convention to use a dotted letter, such
            as $\dot x$, to indicate that we are discussing a $\mathbb P$-name.

            One says that a condition $p\in \mathbb P$ forces a statement
            $\varphi$
              to hold, denoted $p\Vdash \varphi$,
            if that statement holds in $M[G]$ for all $\mathbb P$-generic filters
            with $p\in G$. The forcing theorem states that if $M[G]\models
            \varphi$,
             then there is some $p\in G$ forcing that $\varphi$ holds.
            The following is an immediate consequence of the forcing theorem.

            \begin{lemma*} If $X\in M$ and $\dot x$ is a $\mathbb P$-name,
            then\label{easyname}
             there is a $\tau\subset X\times \mathbb P$, such that
            for any generic $G$, $\tau[G] = X\cap \val_G(\dot x)$.
            \end{lemma*}

            In other words, the family of subsets of any $X\in M$ in
            the extension $M[G]$ is equal to
             $\{ \tau[G] : \tau \subset X\times \mathbb P, \ \
            \tau\in M\ \}$.  We will be using
            the forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
            The elements of this poset are all the finite partial functions
            from $\omega_2$ into $2$ ordered by reverse inclusion.
            It follows that, for any $\lambda\in \omega_2$,
             each of
             $\operatorname{Fn}(\lambda,2)$ and $\operatorname{Fn}(\omega_2\setminus
             \lambda,2)$ are subposets. For any
             $\operatorname{Fn}(\omega_2,2)$-generic
            filter  $G$, it easily follows that $G_\lambda = G\cap
            \operatorname{Fn}(\lambda,2)$ and
             $G^\lambda = G\cap
            \operatorname{Fn}(\omega_2\setminus
             \lambda,2)$ are also generic filters. But a much stronger statement is
             true.

            \begin{lemma*}\cite{MR597342}
            Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a
             generic\label{factor} filter,
             and let $\lambda\in \omega_2$. Then the final model $M[G]$
            is equal to $(M[G_\lambda])[G^\lambda]$ in the sense that
            $G^\lambda$ is a $\operatorname{Fn}(\omega_2\setminus \lambda,
             2)$-generic filter   over the model $M[G_\lambda]$.

            In addition, for each $X\in M$ and name $\dot A\subset
            X\times \operatorname{Fn}(\omega_2,2)$, we get that
             \[ (\dot A(G_\lambda))[G^\lambda] = \dot A [G]\ \ \mbox{where}\
            \dot A(G_\lambda) =
             \{ (x,p\restriction [\lambda,\omega_2))  :
             (x,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \lambda\in G_\lambda\}
            \]
            \end{lemma*}

            With these lemmas in hand we are ready to prove the theorem. The idea
            of the proof comes from  Kunen's result about no $\omega_2$ length mod
            finite chains of subset of $\omega$. We consider any  family of
            names  of suitable one-to-one functions from countable subsets of
            $\omega_2$ into $\omega$. We identify a large enough $\lambda\in \omega_2$
            so that a pattern has emerged and we pass to the model $M[G_\lambda]$. We
            then show that this pattern can not continue out to $\omega_2$.

            \begin{theorem} There exists a model of ZFC for which
             $\mathfrak c=\aleph_2$ and $\lnot \mathcal A(\aleph_2)$.
            \end{theorem}

            \begin{proof}
            We start with a model $M$ of GCH and suppose that $G$ is a
            $\operatorname{Fn}(\omega_2,2)$-generic filter. The argument takes
            place in $M$.
            Let $\{ \dot f_{A} : A\in [\omega_2]^\omega\}$ be a family of
            names (in $M$)
             such that, for any generic $G$ and each $A\in [\omega_2]^\omega\cap
             M$,
             $\dot f_{A}[G]$ is a one-to-one function from $A$ into
            $\omega$.  We also assume that whenever $B\subset A$ are members of
            $[\omega_2]^\omega$, we have that $\dot f_{B}[G]\subset^* \dot
            f_{A}[G]$. If we now obtain a contradiction
            then we will have shown that $\mathcal A(\aleph_2)$ fails.

            By \cite[1.5]{MR1031969}, there is a set $H\subset H(\aleph_3)$
            such that the family $\{ \dot f_{A} : A\in [\omega_2]^{\omega}\}$ is an
            element of $H$,  $H$ is an elementary submodel of
            $ H(\aleph_3)$, $H$ has cardinality
            $\aleph_1$, and $H^\omega\subset H$ (every
             countable subset of $H$ is an element of $H$).

            Let $\lambda = H\cap \omega_2$ (same as the supremum of $H\cap
            \omega_2$). Consider the name  $\dot f_{[\lambda,\lambda+\omega)}$.
            What is such a name?  By Lemma \ref{easyname},
            we can assume that it is a set of pairs
             of the form $( (\lambda+k,m), p)$ where $p\in \mathop{Fn}(\omega_2,
             2)$ and, of course, $k,m\in \omega$.
            Furthermore,  for each $k,m$ it is enough
            (see \cite[5.11,5.12]{MR597342})
            to take a  countable set of such $p$ to get an equivalent
            (\textit{nice}\/) name.
            Given any such nice name $\dot f$, let $\operatorname{supp}(\dot f)$
            denote the union of the domains of conditions $p$ appearing in the
            name.

             Now let $Y$ equal $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\setminus \lambda$. Furthermore,
             fix any $\mu\in \lambda\subset H$ such that
               $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\cap \lambda$ is contained in $\mu$.
             Let $\delta\in \omega_1$ denote the order type of
             $Y$ and let  $\varphi_{\mu,\lambda}$ be the order-preserving function
             from  $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts
             canonically to
            an order-preserving bijection $\varphi_{\mu,\lambda}:
            \operatorname{Fn}(\mu\cup Y,2) \mapsto
            \operatorname{Fn}(\mu+\delta,2)$.
            Now fix any  $\mu<\lambda$ so that
             $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\cap \lambda\subset \mu$.
            We can similarly make sense of the name
             $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_H$.
            Here simply, for each tuple $(\,(k,m), p)\in \dot
            f_{[\lambda,\lambda+\omega)}$,
             we have that $(\,(k,m),\varphi_{\mu,\lambda}(p))$ is in $F_H$.
            Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
            be interpreted in the above sense as giving $F_H$ (which is an element
            of $H$).

             Other values
            replacing $\lambda>\mu$ will result in their own set $Y$
            and canonical map $\varphi_{\mu,\lambda}$.
            Now the object $F_H$ is an
            element of $H$, and $H$ believes this statement is true:
            $$
            (\forall \beta\in\omega_2)~ (\exists \lambda\in \omega_2\setminus \beta)~~~
            \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
            \cap \lambda\subset \mu \ \ \mbox{and}\ \
            F_H = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$$

            But now, this  means that,
            not only is there  an $\alpha\in H$,
            $ F_H = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})$
            but also that there is an increasing sequence
             $\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda$ of
             such $\alpha$'s satisfying that, for each $\xi$
            we have that $\operatorname{supp}(\dot
            f_{[\alpha_\xi,\alpha_\xi+\omega)})$ is contained in $\alpha_{\xi+1}$.

            Choose such a sequence.
             This means that if we let $A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)$ we
             have the name $\dot f_A$ in $H$. This then means that all
             the $( (\beta,m) , p)$ appearing in (the nice name)
            $\dot f_A$ have the property
             that $\mathop{dom}(p)$ is contained in $H$.
            There is, also within $H$, a name $\dot g$ satisfying that
             $\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)$
            for all $k >\dot g(n)$,
            or more precisely,
             $\dot g\subset (\omega\times\omega) \times
             \operatorname{Fn}(\omega_2,2)$ satisfies that
             $\dot g[G]\in \omega^\omega$ and
              $\dot f_{A}[G](\alpha_n+k) = \dot
              f_{[\alpha_n,\alpha_n+\omega)}[G](\alpha+k)$
            for all $k>\dot g[G](n)$.

            We now apply  Lemma \ref{factor} and we are now
            working in the extension $M[G_\mu]$.
            We work for a contradiction. Something special has now happened,
             namely,  the supports of the names $\{
            \dot f_{[\alpha_n, \alpha_n+\omega)} (G_\mu):  0< n<\omega\}$ are pairwise disjoint
            and also disjoint from the support of the name
             $\dot f_{[\lambda,\lambda+\omega)}(G_\mu)$.
             And not only that, these names are pairwise isomorphic (in
             the way that they all map to $F_H$).

             Since $A$ is disjoint from $[\lambda,\lambda+\omega)$,
            there must be an integer $\ell$
            together with a condition
             $q\in \mathop{Fn}(\omega_2\setminus \mu,2)$ satisfying that for all
             $n>\ell$ , $q$ forces that

            \centerline{
             ``if $k>\dot g(n)$ then
             $(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_\mu))(\alpha_n+k) \neq
            (\dot f_{[\lambda,\lambda+\omega)}(G_\mu))(\lambda +k)$''.}

            Choose $n>\ell$ large enough so that $\mathop{dom}(q) \cap [\alpha_n,
            \alpha_{n+1})$ is
            empty.
             Choose $q_1<q\restriction \lambda$ (in $H$) so that
            $$ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
             \dot f_{[\alpha_n,\alpha_n+\omega)}) =
            \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
             \dot f_{[\lambda,\lambda+\omega)}) $$
            and then (again in $H$) choose $q_2 < q_1$
            so that it both forces a value
             $L$ on $\ell+\dot g(n)$
            and subsequently forces a value $m$ on
             $\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)$.
            But now, again calculate
            $$ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
            (q_2\restriction \operatorname{supp}(\dot
            f_{[\alpha_n,\alpha_n+\omega)}))$$
            and, by the isomorphisms, we have that $q_3$ forces that
             $\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m$.

            Technically (or with more care)  all of this is taking place in the
            poset $\operatorname{Fn}(\omega_2\setminus \mu,2)$ and this means
            that $q_3$ and $q$ are  with each other.
            To verify this it suffices to consider
             $q(\beta)=e$ and to assume that $q_3(\beta)$ is defined.
            Since $q_3(\beta)$ is defined, we have that
            there is a  $\beta'\in\mathop{dom}(q_2)$ such that $
             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')$,
            and that $q_3(\beta) = q_2(\beta')$.
            But, by definition of $q_1$, $\beta'\in\mathop{dom}(q_1)$
            and even  that $q_1(\beta') = q(\beta)$.
             Then, since $q_2<q_1$, we have that $q_2(\beta')=q_1(\beta') =
             q(\beta)$. This completes the circle that $q_3(\beta) = q(\beta)$.

            Finally, our contradiction is that $q_3\cup q_2\cup q$
            forces that
             $k=L+1$ violates the quoted statement above.
            \end{proof}

@@

@@

@@

  Note that Question \ref{mainQuestion} remains unsolved; however,
  our results have revealed that we cannot hope to find a \(ZFC\)
  counterexample where \(X=\oneptlind\kappa\). This is
  because if we also assume \(V=L\), it follows that
  \(\alcompSP{\kappa}\) and therefore
  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\)
  for every cardinal \(\kappa\).
  Although, one may consider the following question.

@@
